Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-05-21 Scripts/Initial_Analysis.Rmd
updates on functions tp work in all systems

GetCentroids <- function(taxon_key,
                         year, 
                         data_type = "Catch",
                         ensemble, 
                         # path,
                         Neighbours,
                         eez_centroid){

@@

  Spp_Dist <- read_dbem_ens(
    taxon_key = taxon_key,
    year = year,
    data_type = data_type,
    ensemble = ensemble,
    path = my_path("D",extra_path = "/DBEM")
  )

@@

  #### Creates a data to control computational time (lol!)
    if(file.exists(paste(my_path("R"),"spp_df.csv",sep="")) == FALSE){
    spp_df <- tibble() %>% 
      write_csv(.,
                paste(my_path("R"),"spp_df.csv",sep=""))
  }

  suppressMessages(
    spp_df <- my_path("R",name="spp_df.csv",read = TRUE)
  )
  spp_df <- tibble(taxon_key,
                   ensemble) %>% 
    bind_rows(spp_df) %>% 
    write_csv(.,
              paste(my_path("R"),"spp_df.csv",sep=""))

@@

# Test_centroids <- GetCentroids(taxon_key = 600004,
#              year = year_df$year,
#              # data_type = data,
#              ensemble = 102,
#              # path = path,
#              Neighbours = Neighbours,
#              eez_centroid = eez_centroid
#              )
# head(Test_centroids)
# unique(Test_centroids$ensemble)
# unique(Test_centroids$neigh)
# 
# ggplot(Test_centroids) +
#   geom_line(
#     aes(
#       x = year,
#       y = distance,
#       color = eez_name
#     )
#   )

@@

  # Plot the result, bruh
  # For testing
  ggplot() +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = trend
              )
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-historic_sd$noise,
                    ymax=historic_sd$hist_mean+historic_sd$noise),
                alpha = 0.5,
                fill = "grey50"
    ) +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = historic_sd$hist_mean
              ),
              colour = "grey50"
    ) +
    geom_point(data = subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)),
               aes(
                 x = year,
                 y = trend,
                 colour = "red",
               ),
               shape = 1,
               size = 3
    ) +
    geom_vline(xintercept = 2000,colour="blue",alpha = 0.5) +
    scale_x_continuous(breaks = seq(1950,2100,5)) +
    theme_classic() +
    ggsave("plot_example.jpg",
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = my_path("R")
       )

@@

  # GetTransIndex(
  #   taxon_key = 600004,
  #   ensemble_list = ensemble_list[1:2],
  #   year = year,
  #   Hist_y = 2000,
  #   data_type = "Abd",
  #   Neighbours = Neighbours,
  #   eez_centroid = eez_centroid
  # )

@@

# EEZ list and their centroid of distribution (see chunk 3)
eez_centroid <- my_path("D", extra_path = "Spatial/", name="eez_centroids.csv", read = TRUE)

# Transboundary species and their sharing EEZs (see Palacios-Abrantes et al; FishForVisa)
Transboundary_spp <- my_path("D", extra_path = "Species/", name="Transboundary_spp.csv", read = TRUE) %>% 
  clean_names()

@@

>>>>

GetCentroids <- function(taxon_key,
                         year, 
                         data_type = "Catch",
                         ensemble, 
                         path,
                         Neighbours,
                         eez_centroid
                         ){

  if(Sys.info()[7] == "jepa88"){
      Sys <-FALSE
    }else{
      Sys <- TRUE
    }

@@

  Spp_Dist <- read_dbem_ens(
    taxon_key = taxon_key,
    year = year,
    data_type = data_type,
    ensemble = ensemble,
    path = path,
    my_path = Sys
  )

@@

  #### Creates a data to control computational time (lol!)
    if(file.exists(paste(my_path("R",repo=Sys),"spp_df.csv",sep="")) == FALSE){
    spp_df <- tibble() %>% 
      write_csv(.,
                paste(my_path("R", repo =Sys),"spp_df.csv",sep=""))
  }

  suppressMessages(
    spp_df <- my_path("R",name="spp_df.csv",read = TRUE, repo =Sys)
  )
  spp_df <- tibble(taxon_key,
                   ensemble) %>% 
    bind_rows(spp_df) %>% 
    write_csv(.,
              paste(my_path("R", repo =Sys),"spp_df.csv",sep=""))

@@

# GetCentroids(taxon_key = 600004,
#              year = year_df$year,
#              # data_type = data,
#              ensemble = 102,
#              Neighbours = Neighbours,
#              eez_centroid = eez_centroid
#              )
# head(Test_centroids)
# unique(Test_centroids$ensemble)
# unique(Test_centroids$neigh)
# 
# ggplot(Test_centroids) +
#   geom_line(
#     aes(
#       x = year,
#       y = distance,
#       color = eez_name
#     )
#   )

@@

  # Plot the result, bruh
  # For testing
  ggplot() +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = trend
              )
    ) +
    geom_ribbon(data = mean_sd_index,
                aes(x=year,
                    ymin=historic_sd$hist_mean-historic_sd$noise,
                    ymax=historic_sd$hist_mean+historic_sd$noise),
                alpha = 0.5,
                fill = "grey50"
    ) +
    geom_line(data = mean_sd_index,
              aes(
                x = year,
                y = historic_sd$hist_mean
              ),
              colour = "grey50"
    ) +
    geom_point(data = subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)),
               aes(
                 x = year,
                 y = trend,
                 colour = "red",
               ),
               shape = 1,
               size = 3
    ) +
    geom_vline(xintercept = 2000,colour="blue",alpha = 0.5) +
    scale_x_continuous(breaks = seq(1950,2100,5)) +
    theme_classic() +
    facet_wrap(~neighbour_id)+
    ggsave(paste(taxon_key,"plot_example.jpg",sep="_"),
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = my_path("R", repo = Sys)
       )

@@

  GetTransIndex(
    taxon_key = 600006,
    ensemble_list = ensemble_list,
    year = year_df$year,
    Hist_y = 2000,
    data_type = "Abd",
    Neighbours = Neighbours,
    eez_centroid = eez_centroid
  )

@@

## ----------------- ##
# Data needed for estimating year of emergence
# Note: Use repo = F when running on the Beast or Hall1000
## ----------------- ##

# SAU relations between INDEX and Country's EEZs (see chunk 3)
index_code <- my_path("G", extra_path = "Spatial/SAU/", name="sau_index_code.csv", read = TRUE, repo = F)

# EEZ list and their centroid of distribution (see chunk 3)
eez_centroid <- my_path("D", extra_path = "Spatial/", name="eez_centroids.csv", read = TRUE, repo=F )

# Neighbour list and their respective id (see chunk 3)
Neighbours <- my_path("D", extra_path = "Spatial/", name="Neighbours_eez_id.csv", read = TRUE, repo = F)

# Transboundary species and their sharing EEZs (see Palacios-Abrantes et al; FishForVisa)
Transboundary_spp <- my_path("D", extra_path = "Species/", name="Transboundary_spp.csv", read = TRUE, repo = F) %>% 
  clean_names()

@@

# List of ensemble members
# ensemble_list <- seq(102,103,1) # for testing
ensemble_list <- seq(102,111,1)
